---
title: "lab5package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab5package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lab5package)
```

This package, designed for the fifth lab of the "Advanced Programming in R" LiU course, contains three functions necessary to get data from politicians using the appropriate data and returning with the desired columns.

## dataset_query()

The `dataset_query()` function, retrieves the information from the "data.riksdagen" API containing all the data, without processing it, from the Swedish politicians.

## years_function()

Given a `dataframe` with the `from` and `tom` columns containing dates with format starting with the year, the `years_function()` returns a vector with all the years included in those intervals.

## get_politicians_data()

The `get_politicians_data()`calls the `dataset_query()` and the `years_function()` and ultimately returns a `data.frame` containing the columns we want to extract from the original data, plus an the default columns containing Birth_Year, Sex, Party and Years.  
-  `column_idx` is the argument of the function, it should be a `numeric` vector with the indexes of the columns we'd like to extract. If unspecified, by default will take the columns corresponding to birth year, sex and party.
